Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-28 paper/paper.Rmd
rewrote CLUTO subsection, changed it to "additional ..."

### Spatiotemporal Clustering (skmeans)

The "CLUTO" clustering algorithm by George Karypis is said to be an application "for clustering of low- and high-dimensional datasets and for analyzing the characteristics of the various clusters" [@cluto].

The method can generally be used in {mlr3spatiotempcv} if users cope with the copyright statement of the tool, which restricts usage to non-profit organizations and US government agencies only, and make the application binary available locally.

These restrictions in combination with

- the requirement of a local binary which needs to be downloaded externally and added to a user's system path
- the absent of updates since the year 2007
- a http-only website
- no response from the copyright holder after asking for the current status of the project

led to the decision to not explain and showcase this method in greater detail in this manuscript.
Users are encouraged to visit the help page of the package for this method (`?ResamplingSptCVCluto`) for more information.

@@

>>>>

@@

### Additional partitioning techniques

Considering the wealth and continuing development of spatial and spatiotemporal partitioning techniques for specific applications, we will refrain from providing a complete account of these algorithms. 
At present, \pkg{mlr3spatiotempcv} also supports spatiotemporal partitioning using the versatile CLUTO clustering algorithm [@cluto]. 
CLUTO is available in R through the \pkg{skmeans} package, which provides an interface to a downloadable compiled library with a restriction to non-commercial uses (see `?ResamplingSptCVCluto` in \pkg{mlr3spatiotempcv} for more information).

<!--- FIXME: It sounds like CLUTO can potentially be applied to spatial coordinates, space-time coordinates, or a combinations of coordinates and features. Does mlr3spatiotempcv support this, or is it limited to coordinates? If yes, perhaps this would be worth mentioning: "CLUTO can be used to partition data based on spatial coordinates, space--time coordinates, features, or a combination of these." -->
